Web-based Supplementary Materials for A Space-time Skew-$t$ Model for Threshold Exceedances by Morris, Reich, Thibaud, and Cooley

### 2016-05-24 LaTeX/supplemental-orig.tex
changes to some of the manuscript preparing for revision

% cross-referencing appendices
\usepackage{xr}
\externaldocument{skewt}

@@

\section{Proof that $\lim_{h \rightarrow \infty} \pi(h) = 0$} \label{a:proofsamepartition}
Let $c$ be the midpoint of $\bs_1$ and $\bs_2$.
Define $A$ as the circle centered at $c$ with radius $h / 2$ where $h = ||\bs_1 - \bs_2||$ is the distance between sites $\bs_1$ and $\bs_2$.
Consider a homogeneous spatial Poisson process over $A$ with intensity given by
\begin{align*}
  \mu(A) = \lambda_{PP} |A| = \lambda_{PP} \pi \left(\frac{h}{2}\right)^2 = \lambda_{PPA}^* h^2.
\end{align*}
Consider a partition of $A$ into four regions, $B_1$, $B_2$, $R_1$, $R_2$ as seen in Web Figure \ref{fig:hpp}.
\begin{figure}
  \includegraphics[width=\linewidth]{plots/circles}
  \caption{Illustration of the partition of $A$.}
  \label{fig:hpp}
\end{figure}
Let $N_j$ be the number of knots in $B_j, j = 1, 2$.
Then
\begin{align}
  P(\bs_1 \in P_i, \bs_2 \in P_{j \neq i}) \ge P(N_1 > 0, N_2 > 0)
\end{align}
since knots in both $B_1$ and $B_2$ is sufficient, but not necessary, to ensure that $\bs_1$ and $\bs_2$ are in different partition sets.
By definition of a Poission process, $N_1$ and $N_2$ are independent and thus $P(N_1 > 0, N_2 > 0) = P(N_1 > 0)^2$, and the intensity measure over $B_1$ is given by
\begin{align}
  \mu(B_1) &= \lambda_{PP} |B_1| = \lambda_{PP} \frac{h^2}{4} \left(\frac{2 \pi}{3} - \frac{\sqrt{3}}{2} \right) \nonumber \\
       &= \lambda^*_{PPB1} h^2.
\end{align}
So,
\begin{align}
  P(\bs_1 \in P_i, \bs_2 \in P_{j \neq i}) >= P(N_1 > 0)^2 = [1 - P(N_1 = 0)]^2 = [1 - \exp\left(-\lambda^*_{PPB1} h^2\right)]^2
\end{align}
which goes to 1 as $h$ goes to infinity.

%Then $\bs_1$ and $\bs_2$ are in different partitions almost surely if two or more points are in $A$.
%Let $N(A)$ be the number of points in $A$, and let
%\begin{align*}
%  \mu(A) = \lambda_{PP} |A| = \lambda_{PP} \pi \left(\frac{h}{2}\right)^2 = \lambda_{PP}^* h^2.
%\end{align*}

%
%
%Then
%\begin{align*}
%  P[N(A) \ge 2] &= 1 - P[N(A) = 0] - P[N(A) = 1]\\
%                &= 1 - \exp\{-\lambda h^2\} - \lambda h^2 \exp\{-\lambda h^2\} \\
%                &= 1 - (1 + \lambda h^2) \exp\{-\lambda h^2\}
%\end{align*}
%which goes to one as $h \rightarrow \infty$.

>>>>

% cross-referencing appendices
\usepackage{xr}
\externaldocument{skewt-orig}

@@

\section{Proof that $\lim_{h \rightarrow \infty} \pi(h) = 0$} \label{a:proofsamepartition}
Consider a homogeneous spatial Poisson process with intensity $\mu$.
Define $A$ as the circle with center \hbox{$(\bs_1 + \bs_2) / 2$} and radius $h / 2$.
Then $\bs_1$ and $\bs_2$ are in different partitions almost surely if two or more points are in $A$.
Let $N(A)$ be the number of points in $A$, and let
\begin{align*}
  \mu(A) = \mu |A| = \mu \pi \left(\frac{h}{2}\right)^2 = \lambda h^2.
\end{align*}
Then
\begin{align*}
  P[N(A) \ge 2] &= 1 - P[N(A) = 0] - P[N(A) = 1]\\
                &= 1 - \exp\{-\lambda h^2\} - \lambda h^2 \exp\{-\lambda h^2\} \\
                &= 1 - (1 + \lambda h^2) \exp\{-\lambda h^2\}
\end{align*}
which goes to one as $h \rightarrow \infty$.
